The Astropy Project

### 2017-10-27 main.tex
Update on Overleaf.

The \package{astropy.nddata} subpackage provides three types of functionality: concrete classes for representing multi-dimensional gridded data like CCD images and utilities for manipulating multi-dimensional images and high-level classes that define an interface for representing generic gridded data that is intended primarily for developers of other packages.

The \texttt{CCDData} class provides I/O to FITS files and uses data structures from \astropypkg, like WCS, to represent the contents of a file abstractly. This class supports basic arithmetic operations on image, including error propagation in limited cases and slicing of images that also appropriately slices the image mask and error arrays, if present.

@@

At a higher level, classes are provided which define a minimal interface for gridded data with attributes for accessing metadata, WCS and other common traits. These serve as a useful base for package authors wishing to develop their own classes for specific use cases and as containers for exchanging gridded data.

>>>>

The \package{astropy.nddata} supackage provides three types of functionality: an abstract interface for representing generic arbitary-dimensional datasets intended primarily for developers of other packages and concrete classes building on this interface and utilities for manipulating these kind of datasets.

The \texttt{NDDataBase} class provides the abstract interface for gridded data with attributes for accessing metadata, the world-coordinate system (WCS), uncertainty and other traits. Building on this interface the \texttt{NDData} class provides a minimally working implementation for storing NumPy arrays. These classes serve as useful base for package authors wishing to develop their own classes for specific use cases and as containers for exchanging gridded data.

The concrete classes \texttt{NDDataRef}, \texttt{NDDataArray} and \texttt{CCDData} extend the storing functionality with options to do basic arithmetic (addition, subtraction, multiplication and division) including error propagation in limited cases and slicing of the dataset based on grid coordinates appropriately handling mask, errors, and units, if present. Additionally \texttt{CCDData} also provides I/O from and to FITS files and uses data structures from \astropypkg, like WCS, to represent the contents of a file abstractly.

@@

\inlinecomment{Should we mention that Cutout2D supports WCS to pixel conversions?}
